---
title: "Alcohol vs Seat choice"
author: "Daniel"
date: "Fall 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row you choose to sit in??

## Introduction

$H_0$ There is no difference between the alcohol consumed based on which row you sit in.

$H_A$ There is a difference between the alcohol consumed based on which row you sit in.

## Methods

The response variable is numerical and the explanatory variable is categorical. therefore we use numerical~cat. 

## Results

## Graphical results

### Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  The box plot shows that the back seats drink the most alcohol. Between the front and middle seats, there is very little difference
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

The box plot shows that the seats in the back consume the most amount of alcohol by a large amount. Between the front and middle, there is very little difference.

## Numerical Summarys 


```{r}
favstats(alcohol~Seat,data=davisdata)
```

The data shows that the mean and median of alcohol consumed is about three times more than the middle row and eight times more than the front seats. The back seats drink more alcohol than both middle and front seats combined

## Inferential Tests

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```
The P value is 0.000116 which is less than 0.05. The p value is smaller there for we reject the null hypothesis. This means that there is a difference in the amount of alcohol consumed bassed on where someone is seated.

```{r}
plot(TukeyHSD(model1))
```

We do not have evidence that there is a difference in the alcohol consumption between the middle and front rows. The only difference we found was that the back row consumes more alcohol than the front and middle rows.

## Conclusions

Is there a difference between the alcohol consumed between the row you choose to sit in? In our findings there was a difference in alcohol consumed based on where you are seated. The data shows that the back row consumes a substantial amount of alcohol compared to the front and middle rows. The p value is 1.16e^-4, smaller than 0.05, which means we reject the null hypothesis of there being no difference in alcohol cosmued based on where you are seated.
