---
title: "Alcohol vs Seat choice"
author: "Daniel"
date: "Fall 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row you choose to sit in??

## Introduction

$H_0$ There is no difference between the alcohol consumed based on which row you sit in.

$H_A$ There is a difference between the alcohol consumed based on which row you sit in.

## Methods

The response variable is numerical and the explanatory variable is categorical. therefore we use numerical~cat. 

## Results

### Graphical results

### Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  The box plot shows that the back seats drink the most alcohol. Between the front and middle seats, there is very little diffrence
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

The box plot shows that the seats in the back consume the most amount of alcohol by a large amount. Between the front and middle, there is very little difference.

## Numerical Summarys 

## Inferential Tests

## Conclusions


